BivData Setup

### 2020-02-10 doc/Results.rmd
add motivating sents to v2 outline

@@

#this first one is the 'first' MLH1 count
#which is this variable

@@

#mean is the new calculated-- mean 0CO is significant and intercept
#oopp <-  lm( mean.MLH1.foci ~ per0CO+ per1CO +per2CO +per3CO, data = #proportion_stats_category)

#summary(oopp)
#not sure if these are inter-correlated
#I don't know why 0COs and the intercept are significant..
#0CO and 1CO are significant when only chrm classes are included (and intercept)

#no longer significant when used
#lm regression indicates that the proportions aren't significant contributers to meanMLH1 -- but this could be due to error
#after added more MSM data, tot_biv is not significant
#0CO is now more significant, and 2CO is sightly significant

#2CO proportion is the most significant, 1CO is second most significat, 3CO doesn't have enough power - total bivalents is also significant, there might be a bias

#MSM needs more bialent observations
#use melt to put all propotions 
#display / visualize / compare proportions
#the table needs to be melted, because it's split by category

@@

<!--Brief lit review for SC length and MLH1 expections. -->

@@

@@

@@

There are a few traits that fall within the CO positions

- 1CO normalized position

- sis.co.ten (sorta interference)

- centromere and telomere distance

**Heterochiasmy**

  B) **sis**ter **co**hesion **ten**sion (sis-co-ten) will be sexually dimorphic as it reflects the general property of unifrom vs telomere/biased CO positioning.

# Q1. Normalized 1CO positions

**for all the test blocks below, integrate the 3 other metrics; siscoten, telomere, centromere distance.

@@

>>>>

#2 sample prop test
prop.test(x, y)

x - list of the number of 'successes' across groups  (1COs)
y - list of the number of 'failures' across groups  (2COs)

(does a chi square test)

@@

#prop.test(x, y)  x number of successes, y total  
#strain sums of n
#look up continuity correction

Mouse.Table_BivData_4MM <- Mouse.Table_BivData_4MM[(!is.na(Mouse.Table_BivData_4MM$mouse)),]

female.mouse.av <-  Mouse.Table_BivData_4MM %>%  filter(sex == "female")
male.mouse.av <-  Mouse.Table_BivData_4MM %>%  filter(sex == "male")

n1CO_list_F <- c( female.mouse.av$n1CO)
n1CO_list_M <- c( male.mouse.av$n1CO)

total_biv_F_list <- c( female.mouse.av$tot.biv)
total_biv_M_list <- c( male.mouse.av$tot.biv)

nbiv_total_list <- c(Mouse.Table_BivData_4MM$tot.biv)

prop.test(n1CO_list_F, total_biv_F_list )

#perform test across strain

Chrm.prop_strain_table <- ddply(Mouse.Table_BivData_4MM, c("strain","sex"), summarise,

                  nbiv = sum(tot.biv ),              
                 n0CO = sum(n0CO ),
                  n1CO = sum(n1CO ),
                 n2CO = sum(n2CO ),
                  n3CO = sum(n3CO )

chrm.prop.strain.female <-  Chrm.prop_strain_table %>%  filter(sex == "female")

female.0CO.prop.test <- prop.test(chrm.prop.strain.female$n0CO, chrm.prop.strain.female$nbiv )
female.1CO.prop.test <- prop.test(chrm.prop.strain.female$n1CO, chrm.prop.strain.female$nbiv )
female.2CO.prop.test <- prop.test(chrm.prop.strain.female$n2CO, chrm.prop.strain.female$nbiv )

chrm.prop.strain.male <-  Chrm.prop_strain_table %>%  filter(sex == "male")
#chrm.prop.strain.male.high.rec <-  Chrm.prop_strain_table %>%  filter(sex == "male")
#chrm.prop.strain.male.low.rec <-  Chrm.prop_strain_table %>%  filter(sex == "male")

male.0CO.prop.test <- prop.test(chrm.prop.strain.male$n0CO, chrm.prop.strain.male$nbiv )
male.1CO.prop.test <- prop.test(chrm.prop.strain.male$n1CO, chrm.prop.strain.male$nbiv )
male.2CO.prop.test <- prop.test(chrm.prop.strain.male$n2CO, chrm.prop.strain.male$nbiv )

@@

#mean is the new calculated-- mean 0CO is significant and intercept
#oopp <-  lm( mean.MLH1.foci ~ per0CO+ per1CO +per2CO +per3CO, data = #proportion_stats_category)
#summary(oopp)
#not sure if these are inter-correlated
#I don't know why 0COs and the intercept are significant..
#0CO and 1CO are significant when only chrm classes are included (and intercept)
#no longer significant when used
#lm regression indicates that the proportions aren't significant contributers to meanMLH1 -- but this could be due to error
#after added more MSM data, tot_biv is not significant
#0CO is now more significant, and 2CO is sightly significant
#2CO proportion is the most significant, 1CO is second most significat, 3CO doesn't have enough power - total bivalents is also significant, there might be a bias
#MSM needs more bialent observations
#use melt to put all propotions 
#display / visualize / compare proportions
#the table needs to be melted, because it's split by category

@@

<!--Brief lit review for SC length and MLH1 expections.
add XX adjusment / arguments
-->

@@

#### Q1. SC Length t.test

@@

#### XX adjustment

Generate inteligible summaries for the permutation / subsampling results.

```{r Q1_XX.adjustment, echo=FALSE}

@@

There are a few traits that fall within the CO positions  
- 1CO normalized position  
- sis.co.ten (sorta interference)  
- centromere and telomere distance  
**Heterochiasmy**

2.A) Normalized 1CO positions will be sexually dimorphic (sedell and Kirkpatrick). 
  B) **sis**ter **co**hesion **ten**sion (sis-co-ten) will be sexually dimorphic as it reflects the general property of unifrom vs telomere/biased CO positioning.
  C) Centromere and telomere distances will be sexually dimorphic.
**for all the test blocks below, integrate the 3 other metrics; siscoten, telomere, centromere distance.
-->

@@

```{r Q1.mean.nrmF1_table, echo=FALSE,eval=FALSE}

#make a table for the sex specific values of the normalized F1 positions

#for strain, sex -- Curated_BivData
#or (Mouse.Table_BivData_4MM)
#norm.first.foci.pos

Q1.normF1.pos_table <- ddply(Mouse.Table_BivData_4MM, c("strain","sex"), summarise,

                    mean_1CO_nrm.pos = mean(norm.first.foci.pos, na.rm = TRUE), 
                  n1CO = sum(n1CO )

### 2020-02-10 src/BivData_Setup.Rmd
add motivating sents to v2 outline

#is there a way that the above table would be different than the 
Mouse.Table_BivData_4MM <- ddply(Curated_BivData, c("mouse"), summarise,
                        Nmice = length(unique(mouse)),
                        Ncells  = length(Obj.ID),

@@

@@

#remove all the non-used strains!!
Mouse.Table_BivData_4MM <- Mouse.Table_BivData_4MM[Mouse.Table_BivData_4MM$strain != "AST",]
Mouse.Table_BivData_4MM <- Mouse.Table_BivData_4MM[Curated_BivData$strain != "TOM",]
Mouse.Table_BivData_4MM <- Mouse.Table_BivData_4MM[Mouse.Table_BivData_4MM$strain != "CZECH",]
Mouse.Table_BivData_4MM$strain <- droplevels(Mouse.Table_BivData_4MM$strain)
#MOLF

#These shouldn't be needed for now.

@@

>>>>

#is there a way that the above table would be different than the 
Mouse.Table_BivData_4MM <- ddply(Curated_BivData, c("mouse"), summarise,
                        Nmice = length(unique(mouse)),
                        Ncells  = length(  unique(fileName) ),
                      tot.biv = length(Obj.ID),

                      n0CO = sum( (hand.foci.count == 0), na.rm = TRUE ),
                      n1CO = sum( (hand.foci.count == 1), na.rm = TRUE ),
                      n2CO = sum( (hand.foci.count == 2), na.rm = TRUE ),
                      n3CO = sum( (hand.foci.count == 3), na.rm = TRUE ),

@@

              mean.telo.dist = mean(telo_dist, na.rm=TRUE),
              mean.cent.dist = mean(dis.cent, na.rm=TRUE)
)
Mouse.Table_BivData_4MM <- Mouse.Table_BivData_4MM[(!is.na(Mouse.Table_BivData_4MM$mouse)),]

@@

#remove all the non-used strains!!
Mouse.Table_BivData_4MM <- Mouse.Table_BivData_4MM[Mouse.Table_BivData_4MM$strain != "AST",]
Mouse.Table_BivData_4MM <- Mouse.Table_BivData_4MM[Curated_BivData$strain != "TOM",]
Mouse.Table_BivData_4MM <- Mouse.Table_BivData_4MM[Mouse.Table_BivData_4MM$strain != "CZECH",]
Mouse.Table_BivData_4MM$strain <- droplevels(Mouse.Table_BivData_4MM$strain)

@@

                      n0CO = sum( (hand.foci.count == 0), na.rm = TRUE ),
                      n1CO = sum( (hand.foci.count == 1), na.rm = TRUE ),
                      n2CO = sum( (hand.foci.count == 2), na.rm = TRUE ),
                      n3CO = sum( (hand.foci.count == 3), na.rm = TRUE ),
